\documentclass[a4paper,3pt]{article}

\usepackage{parskip} 
\usepackage{hologo}
\usepackage{fontspec}

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9, top=.1in, bottom=.1in]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.42\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{-1pt}{1pt}{2pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\color[HTML]{110223}%{1C033C}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}
% \usepackage{times}

% For underline
\usepackage[normalem]{ulem}

\setmainfont{Arial}  % Set it to whatever you like

\begin{document}


% non-numbered pages
\pagestyle{empty} 


\begin{tabularx}{\linewidth}{@{} C @{}}
\color[HTML]{1C033C} \HugeSai Jetti \\[0.5pt]
\\
{\href{mailto: venkatj2@umbc.edu}{\raisebox{-0.05\height}{\faEnvelope} venkatj2@umbc.edu} $|$}
{\href{tel:+12404575305}{\raisebox{-0.05\height}{\faMobile} +12404575305}  $|$}
{\href{https://www.linkedin.com/in/sai-jetti}{\raisebox{-0.05\height}{\faLinkedin} https://www.linkedin.com/in/sai-jetti}}
\end{tabularx}

\section{Summary}
Experienced in developing scalable backend systems, microservices, and cloud-based solutions using Java, Python, Golang, and AWS. Skilled in building RESTful APIs, optimizing system performance, automating deployments with Kubernetes and CI/CD, and integrating LLM-powered applications for intelligent data processing.

%Experience
\section{Experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{{TechCorp}} \hfill  Jan 2020 - Present \\[2pt]
\textbf{\textit{Software Engineer}}\ \hfill  \textit{Java, Spring Boot, AWS, SQL, RESTful API} \\[2pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item Developed and optimized RESTful APIs using Java (Spring Boot) to enhance data retrieval efficiency, reducing response time by 35%.
\item Integrated AWS services such as S3, Lambda, and RDS to build scalable backend solutions and improve cloud adoption.
\item Designed and implemented database schemas in PostgreSQL, improving data integrity and query performance by 40%.
\item Implemented authentication and authorization using Spring Security and JWT, strengthening system security.
\item Built event-driven microservices with Apache Kafka by implementing Spring Boot Kafka producers & consumers.
\item Assisted in containerizing microservices using Docker and deploying them to AWS ECS, improving scalability.
    \end{itemize}
\end{minipage}
\end{tabularx}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{{Data Inc.}} \hfill  Jun 2019 - Dec 2019 \\[2pt]
\textbf{\textit{Intern}}\ \hfill  \textit{Python, Flask, MongoDB, Docker} \\[2pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item Developed a Flask-based web application for data visualization, improving user engagement by 50%.
\item Implemented RESTful APIs for data retrieval and manipulation, enhancing system performance.
\item Containerized the application using Docker for consistent deployment across environments.
    \end{itemize}
\end{minipage}
\end{tabularx}

% Education
\section{Education}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\color[HTML]{1C033C} \textbf{University of Maryland, Baltimore County} & \hfill  Aug 2018 - May 2020 \\
\textbf{Master of Science in Computer Science} & \hfill \textit{\textbf{GPA: 3.8/4.0}} \\
\multicolumn{2}{@{}X@{}}{\textbf{Courses}: Java, Python, AWS, SQL, Machine Learning.}
\end{tabularx}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\color[HTML]{1C033C} \textbf{RVR&JCCE, India} & \hfill  Aug 2017 - Jul 2021 \\
\textbf{BTech in ECE} & \hfill \textit{\textbf{GPA: 9.02/10}} \\
\multicolumn{2}{@{}X@{}}{\textbf{Courses}: Data Structures, Algorithms, Operating Systems, Computer Networks.}
\end{tabularx}

\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{LLM-Powered Chatbot} \hspace*{69ex} Jan 2023 - Apr 2023\\[2pt]
\textbf{\textit{Developed a chatbot using LLMs for intelligent data processing and user interaction using python, flask, and AWS.}} \hfill\\[2pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item Developed a chatbot using LLMs for intelligent data processing and user interaction.
\item Integrated with RESTful APIs for real-time data retrieval and processing.
\item Implemented CI/CD pipelines for automated deployment using Jenkins and Docker.  
    \end{itemize}
    \end{minipage}
\end{tabularx}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{E-commerce Web Application} \hspace*{69ex} May 2022 - Aug 2022\\[2pt]
\textbf{\textit{Designed and developed a full-stack e-commerce application using Java, Spring Boot, and React.}} \hfill\\[2pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item Designed and developed a full-stack e-commerce application using Java, Spring Boot, and React.
\item Implemented RESTful APIs for product management, user authentication, and payment processing.
\item Deployed the application on AWS using EC2 and RDS.  
    \end{itemize}
    \end{minipage}
\end{tabularx}


\section{Technical Skills}
\begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=1pt]
\item \textbf{Languages}
\hspace*{18.5ex}                  Java, SQL, Python, JavaScript, Go.
\item \textbf{Frameworks and Packages}
 \hspace*{4ex} Springboot, Angular, Mockito, MySQL, Neo4j, PostgreSQL, Scikit Learn, Pytorch.
\item\textbf{Cloud and Databases}
 \hspace*{9.2ex} AWS (SageMaker, Lambda, EC2), Snowflake, MySQL, MongoDB.
 \item\textbf{Tools}
 \hspace*{23.8ex} Gerrit, Git, Docker, Kubernetes, AWS, Linux, REST APIs, Postman, Jenkins.
\item\textbf{Big Data and ETL Tools}
 \hspace*{7.3ex} Apache Spark, Hadoop, kafka, Airflow, Apache Nifi, Pentaho.
 \end{itemize}
\end{document}