\documentclass[a4paper,3pt]{article}

\usepackage{parskip} 
\usepackage{hologo}
\usepackage{fontspec}

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9, top=.1in, bottom=.1in]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.42\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{-1pt}{1pt}{2pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\color[HTML]{110223}%{1C033C}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}
% \usepackage{times}

% For underline
\usepackage[normalem]{ulem}

\setmainfont{Arial}  % Set it to whatever you like

\begin{document}


% non-numbered pages
\pagestyle{empty} 


\begin{tabularx}{\linewidth}{@{} C @{}}
\color[HTML]{1C033C} \Huge{{NAME}} \\[0.5pt]
\\
{\href{mailto: {{MAILID}}}{\raisebox{-0.05\height}{\faEnvelope} {{MAILID}}} $|$}
{\href{tel:+1{{PHONE}}}{\raisebox{-0.05\height}{\faMobile} +1{{PHONE}}}  $|$}
{\href{{{LINKEDIN}}}{\raisebox{-0.05\height}{\faLinkedin} {{LINKEDIN}}}}
\end{tabularx}

\section{Summary}
{{SUMMARY}}

%Experience
\section{Experience}

{{EXPERIENCE}}

% Education
\section{Education}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\color[HTML]{1C033C} \textbf{UNIVERSITY OF MARYLAND,
BALTIMORE COUNTY} & \hfill  May 12, 2025 \\
\textbf{MS in Data Science} & \hfill \textit{\textbf{GPA: 4.0 /4.0}} \\
\multicolumn{2}{@{}X@{}}{\textbf{Courses}: LLM(Transformers, RAG, Fine Tuning, Prompt Engineering), Big Data Processing, Machine Learning.}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
 \textbf{RVR \& JC College of Engineering} & \hfill Jul 2017 - Jul 2021 \\
 \textbf{Bachelor of Technology in Electronics and Communication Engineering} & \hfill \textit{\textbf{GPA: 9.02 /10}} \\
\multicolumn{2}{@{}X@{}}{\textbf {Courses}: Analysis and Design of Algorithms, DataBase Design, Java Programming, Web Development, Data Structures, Object Oriented Programming, HDL Programming, Verilog.}
\end{tabularx}

\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Flight Management System} \hspace*{69ex} Nov 2024\\[2pt]
\textbf{\textit{Backend Development for Booking and Managing Flights using Java, Spring Boot, Hibernate, MySQL}} \hfill\\[2pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item Designed and implemented RESTful APIs to support core functionalities, including flight booking, cancellation, schedule management, and user registration/login.
\item Utilized Spring MVC for controller logic and Hibernate/JPA for object-relational mapping, efficient database interactions.
\item Built role-based access controls, enabling administrators to manage flight schedules, airport information, and user data.
\item Integrated real-time flight data from multiple airline carriers to provide up-to-date flight details and pricing for users.    
    \end{itemize}
    \end{minipage}
\end{tabularx}


\section{Technical Skills}
\begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=1pt]
\item \textbf{Languages}
\hspace*{18.5ex}                  Java, SQL, Python, JavaScript, Go.
\item \textbf{Frameworks and Packages}
 \hspace*{4ex} Springboot, Angular, Mockito, MySQL, Neo4j, PostgreSQL, Scikit Learn, Pytorch.
\item\textbf{Cloud and Databases}
 \hspace*{9.2ex} AWS (SageMaker, Lambda, EC2), Snowflake, MySQL, MongoDB.
 \item\textbf{Tools}
 \hspace*{23.8ex} Gerrit, Git, Docker, Kubernetes, AWS, Linux, REST APIs, Postman, Jenkins.
\item\textbf{Big Data and ETL Tools}
 \hspace*{7.3ex} Apache Spark, Hadoop, kafka, Airflow, Apache Nifi, Pentaho.
 \end{itemize}
\end{document}